Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2021-06-23 doc/manuscript/ESSDmanuscript.Rmd
start variable mapping table

@@

Mapping is shown in Fig. 1

>>>>

```{r table_ForCfieldmapping, eval = TRUE, echo=FALSE, warning=FALSE}

ForC_variables_included <- read.csv("figures_tables/ForC_variables_included.csv")
names(ForC_variables_included) <- stringr::str_replace_all(names(ForC_variables_included), "\\.", " ")

library(knitr)
library(kableExtra)
knitr::kable(ForC_variables_included, format = "latex",
             longtable = FALSE,
             caption = "\\textbf{Mapping of ForC fields to EFDB.}") %>%
  kableExtra::kable_styling(full_width = TRUE) %>%
  row_spec(0, bold = TRUE)
```

@@

Mapping of variables is shown in Fig. 1

### 2021-06-23 doc/manuscript/ESSDmanuscript.tex
start variable mapping table

>>>>

\caption{\label{tab:table_ForCfieldmapping}\textbf{Mapping of ForC fields to EFDB.}}
\centering
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\hline
\textbf{Table} & \textbf{Variable} & \textbf{EFDB field} & \textbf{Use} & \textbf{Required}\\
\hline
Sites &  & NA &  & \\
\hline
Measuremennts &  & NA &  & \\
\hline
 & sd, se, lower95\%CI, upper 95\%CI & NA &  & y\\
\hline
 & mean.in.original.units, original.units & NA &  & y\\
\hline
 & data.location.within.source & NA & confirm that data weren't digitized, facilitate finding data in original publication & y\\
\hline
PFT & description & NA &  & \\
\hline
 &  & NA &  & \\
\hline
Citations & (several fields) & NA &  & \\
\hline
\end{tabu}
\end{table}
